Analysis2

### 2023-11-03 Lahman Analysis/Rough Analysis 2/Analysis2.qmd
Progress from meeting

@@

>>>>

### 11/3 meeting

```{r}
by_park <- Batting %>% 
  group_by(yearID, park) %>% 
  summarize(HR = sum(HR), AB = sum(AB)) %>% 
  mutate(park_index = as.integer(park))
```

```{r}
data26c <- list(
  N = nrow(by_park),
  n_year = n_distinct(by_park$yearID),
  n_park = n_distinct(by_park$park_index),
  AB = by_park %>% pull(AB),
  HR = by_park %>% pull(HR),
  park = by_park %>% pull(park_index),
  Year = by_park %>% pull(yearID) -1972
)
```

```{r}
fit26c <- stan(
  file = "HR26c.stan",
  data = data26c,
  iter = 2000
)
```

```{r}
print(fit26c, pars = "b")
```

```{r}
traceplot(fit26c)
```

```{r}
saveRDS(fit26c, "HR26c.rds")
```

```{r}
year_and_stadium_age <- Batting %>% 
  group_by(yearID, park, Age) %>% 
  summarize(HR = sum(HR), AB = sum(AB)) %>% 
  mutate(park_index = as.integer(park)) %>% 
  mutate(cAge = Age - 30, .after = Age)
```

```{r}
data26d <- list(
  N = nrow(year_and_stadium_age),
  n_year = n_distinct(year_and_stadium_age$yearID),
  n_park = n_distinct(year_and_stadium_age$park_index),
  AB = year_and_stadium_age %>% pull(AB),
  HR = year_and_stadium_age %>% pull(HR),
  park = year_and_stadium_age %>% pull(park_index),
  Year = year_and_stadium_age %>% pull(yearID) -1972,
  cAge = year_and_stadium_age %>% pull(cAge)
)
```

```{r}
fit26d <- stan(
  file = "HR26d.stan",
  data = data26d,
  iter = 200
)
```

```{r}
summary(fit26d, 'beta1')$summary
```

@@

```{r}
ggplot(sum_all_years_park)+
  geom_histogram(aes(x = park))
```
